\textbf{Case Studies II - Community Talks}

### 2013-04-09 ricardogarfe/final_report/004-mozilla-community-talk.tex
Update 004-mozilla-community-talk.tex
I think it is better to color the links or made them more emphases by bold or italic

\par \textit{"Our mission is to promote openness, innovation \& opportunity on the Web."} In \href{http://www.mozilla.org/about/manifesto.html}{Mozilla Manifesto} you can read the whole document about freedom and accesibility that they apply day by day.

@@

\begin{itemize}
	\item \textit{Firefox} - Web Browser with a particularity that doesn't have portability to IOS because it uses Gecko instead of Webkit to render content. Apple doesn't allow a browser (or anyhting) that is not reder usgin Webkit.
	\item \textit{FirefoxOS} - New Mobile operative system based in HTML5 and Browser Oriented.
	\item \textit{Thunderbird} - eMail management but abandoned project. Developers have changed to Mozilla.
	\item \textit{Camino} - MacOS Mozilla Browser using Webkit
	\item \textit{Seamonkey} - Firefox, Thunderbird, Chat, Web Editor.
	\item \textit{Sundbird/Lightning} - Calendar project from Mozilla.
	\item \textit{XULRunner} - It's like Java Virtual Machine allowing multiplatform products oriented to Mozilla packages.
\end{itemize}

@@

\begin{itemize}
	\item \textit{Mailing lists}- For developers, information, everything related to \href{https://lists.mozilla.org/listinfo}{Mozilla}.
	\item \textit{Bug Tracking System}-\href{https://bugzilla.mozilla.org/}{Bugzilla}for every product.
	\item \textit{Source Code Managemet}- Baazar, Mercurial, SVN, CVS.
	\item \textit{MXR}- Cross references about the code from Mozilla (\href{http://mxr.mozilla.org/}{mxr}).
	\item \textit{Forge for scm}- GitHub.
	\item \textit{QMO}-Home of Mozilla's testing and\href{http://quality.mozilla.org/}{quality assurance community}.
	\item \textit{Crash Stats} - \emph{Continuous integration} server output visualizations using\href{https://github.com/mozilla/socorro}{Socorro}.
	\item \textit{Graph CI}- Graphic visualization for every built from the code in\href{http://graphs.mozilla.org/}{graph section}.
	\item \textit{Tinderbox}- Tool to navigate through\href{http://tinderbox.mozilla.org/showbuilds.cgi}{build logs and results}.
\end{itemize}

@@

\par Furthermore gives you the opportunity to look for contribution near your location, a very useful tool. Mozilla invites you to be part of an Open Web. You don't have to be the smartest guy in the world they do this work spreading that all help is good an they will find for you the best place to help \textit{everyone}with your contribution.

>>>>

\par \textit{"Our mission is to promote openness, innovation \& opportunity on the Web."} In \href{http://www.mozilla.org/about/manifesto.html}{Mozilla Manifesto} you can read the whole document about freedom and accessibility that they apply day by day.

@@

\begin{itemize}
	\item \textit{Firefox} - Web Browser with a particularity that doesn't have portability to IOS because it uses Gecko instead of Webkit to render content. Apple doesn't allow a browser (or anything) that is not reder using Webkit.
	\item \textit{FirefoxOS} - New Mobile operative system based in HTML5 and Browser Oriented.
	\item \textit{Thunderbird} - eMail management but abandoned project. Developers have changed to Mozilla.
	\item \textit{Camino} - MacOS Mozilla Browser using Webkit
	\item \textit{Seamonkey} - Firefox, Thunderbird, Chat, Web Editor.
	\item \textit{Sundbird/Lightning} - Calendar project from Mozilla.
	\item \textit{XULRunner} - It's like Java Virtual Machine allowing multiplatform products oriented to Mozilla packages.
\end{itemize}

@@

\begin{itemize}
	\item \textit{Mailing lists}- For developers, information, everything related to \href{https://lists.mozilla.org/listinfo}{Mozilla}.
	\item \textit{Bug Tracking System}-\href{https://bugzilla.mozilla.org/}{Bugzilla}for every product.
	\item \textit{Source Code Management}- Baazar, Mercurial, SVN, CVS.
	\item \textit{MXR}- Cross references about the code from Mozilla (\href{http://mxr.mozilla.org/}{mxr}).
	\item \textit{Forge for scm}- GitHub.
	\item \textit{QMO}-Home of Mozilla's testing and \href{http://quality.mozilla.org/}{quality assurance community}.
	\item \textit{Crash Stats} - \emph{Continuous integration} server output visualizations using \href{https://github.com/mozilla/socorro}{Socorro}.
	\item \textit{Graph CI}- Graphic visualization for every built from the code in\href{http://graphs.mozilla.org/}{graph section}.
	\item \textit{Tinderbox}- Tool to navigate through \href{http://tinderbox.mozilla.org/showbuilds.cgi}{build logs and results}.
\end{itemize}

@@

\par Furthermore gives you the opportunity to look for contribution near your location, a very useful tool. Mozilla invites you to be part of an Open Web. You don't have to be the smartest guy in the world they do this work spreading that all help is good an they will find for you the best place to help \textit{everyone} with your contribution.
